Can historical data predict population responses to climate change experiments?

### 2016-12-18 precip/manuscript/precip_ms.tex

\subsection*{Quantifying predictive accuracy}

After fitting the year effects and climate models to the observational data, we generated predictions from these models for each of the vital rates in the experimental plots. We then assessed performance of the climate and null models by calculating the mean square error (MSE) between the predicted and observed responses in the experimental data as,

@@

During the course of our experiment annual precipitation recorded at the local climate station varied from X to X percent of period of record averages (1925 to 2016).  The year of X was exceptionally dry while the year of X was.  The precipitation during the summer of X was the wettest on record.  Mean annual average air temperature during this period were consistently well above average for the period of record, with the years of X X and X being among the warmest ever recorded at this site.

@@

While our climate models failed to improve predictions, we did find that they predicted treatment responses that were largely in the same direction as the observed treatment responses (fig).  The overall correlation between the predicted treatment parameters and the observed treatment parameters was X with stronger correlation for the climate effects on the size by treatment effects fit for \textit{P. secunda} growth and survival and \textit{A. tripartita} growth (fig).  A table of MSE between predicted and expected treatment parameters shows that averaged over all species and vital rates, we did the best job of predicting the response to the drought treatment.  Averaged across all treatements and vital rates, we did the best job predicting the response of \textit{species} to the treatments. Finally if we average across all species and treatments, we did the best job of predicting VR parameters in response to the treatment.

As for the vital rate predictions, our one-step ahead cover predictions from the year effects models and the climate models were fairly similar (fig). Models with and without soil moisture parameters tended to underpredict the cover of \textit{A. tripartita} and \textit{P.secunda} during the experiment (fig).  When we compare the MSE of the predicted population growth rates for each year and quadrat from the model with and without the soil moisture parameters, we find that adding soil moisture to the vital rate models always made the one step ahead cover predictions slightly less accurate (table).  The pattern when we consider the correlation between the predicted and observed population growth rates was slightly different (table?).  When we broke the population growth rate data up by treatment, we found that adding soil moisture to the models mostly did not improve predictions of cover change in the control and irrigation plots.  However, including the soil moisture parameters led to better predictions of changes in population growth rates for three of the species (S , S, and S) in the drought plots (fig).

>>>>

\subsection*{Quantifying predictive accuracy} 
After fitting the year effects and climate models to the observational data, we generated predictions from these models for each of the vital rates in the experimental plots. We then assessed performance of the climate and null models by calculating the mean square error (MSE) between the predicted and observed responses in the experimental data as,

@@

@@

While our climate models failed to improve predictions, we did find that they predicted treatment responses that were largely in the same direction as the observed treatment responses (fig).  The overall correlation between the predicted treatment parameters and the observed treatment parameters was X with stronger correlation for the climate effects on the size by treatment effects fit for \textit{P. secunda} growth and survival and \textit{A. tripartita} growth (fig) than for the treatment effects on the intercept.  A table of MSE between predicted and expected treatment parameters shows that averaged over all species and vital rates, we did the best job of predicting the response to the drought treatment.  Averaged across all treatements and vital rates, we did the best job predicting the response of \textit{species} to the treatments. Finally if we average across all species and treatments, we did the best job of predicting VR parameters in response to the treatment.

As for the vital rate predictions, our one-step ahead cover predictions from the year effects models and the climate models were fairly similar (fig). Models with and without soil moisture parameters tended to underpredict the cover of \textit{A. tripartita} and \textit{P.secunda} during the experiment (fig).  When we compare the MSE of the predicted population growth rates for each year and quadrat from the model with and without the soil moisture parameters, we find that adding soil moisture to the vital rate models always made the one step ahead cover predictions slightly less accurate (table).  The pattern when we consider the correlation between the predicted and observed population growth rates was slightly different (table?).  When we considered the population growth rate data separately by treatment, we found that adding soil moisture to the models mostly did not improve predictions of cover change in the control and irrigation plots. However, we did find that adding soil moisture parameters produced better predictions of population growth rates for three of the species (S , S, and S) in the drought plots (fig).
